---
title: "2025-02-18"
author: "John Hinkle"
format: html
editor: visual
---

# February 18th, 2025 Notes

## In

```{r}
library(mosaic)
mu <- 10 # "mean" parameter
sigma <- 2 # "standard deviation" parameter
plotDist("norm", mean=mu, sd=sigma, xlab="x", ylab="Frequency")
```

## Draw a random sample of 10 out of the normal distribution

```{r}
s1 <- rnorm (n = 10, mean = 10, sd = 2)
mean(s1) # the mean of the random sample
```

## Draw a random sample of 10 out of the Poisson distribution

```{r}
s2 <- rpois(n = 10, lambda = 10)
mean(s2)
```

## Sampling distributions

```{r}
# number of replicates
reps <- 500

# generates a sampling distribution for the mean of a sample with the specified parameters
samp_dist_mean <- do(reps) * mean(rnorm(n = 10, mean = 10, sd = 2))

# generates a sampling distribution for the median of a sample with the specified parameters
samp_dist_median <-do(reps) * median(rnorm(n = 10, mean = 10, sd = 2))

```

## Plot histograms of sample distributions for stats

Sample size influences error of estimating mean (and median). Larger sample = narrower distribution/less error.

```{r}
# mean
histogram(samp_dist_mean$mean)

# median
histogram(samp_dist_median$median)
```

## Standard deviation and standard error

```{r}
x <- rnorm(n = 10, mean = 10, sd = 2)
sd <- sd(x) # std dev
se <- sd/sqrt(length(x)) # std error
print(paste("The standard deviation is", sd))
print(paste("The standard error is", se))
```

## Confidence interval

Interval around our estimate of the mean of the sampling distribution for a particular statistic (typically the mean).

95% confidence interval = 95% chance statistic of a re-sample of the population falls within the interval.

## In-Class Exercise

### Sample of 100 from normal distribution

```{r}
norm_dist <- rnorm(n = 100, mean = 2, sd = 4)
```

### Mean

```{r}
mean(norm_dist)
```

### Standard deviation

```{r}
print(stdev <- sd(norm_dist))
```

### Standard error

```{r}
print(stderr <- stdev/sqrt(length(norm_dist)))
```

### Draw 100 samples for mean

```{r}
# number of replicates
reps_100 <- 100

# generates a sampling distribution for the mean of a sample with the specified parameters
sample_dist_mean_100 <- do(reps_100) * mean(rnorm(n = 100, mean = 2, sd = 4))
print(se_100 <- sd(sample_dist_mean_100$mean))
```

### Draw 1000 samples for mean

```{r}
# number of replicates
reps_1000 <- 1000

# generates a sampling distribution for the mean of a sample with the specified parameters
sample_dist_mean_1000 <- do(reps) * mean(rnorm(n = 100, mean = 2, sd = 4))
print(se_1000 <- sd(sample_dist_mean_1000$mean))
```

### Draw 20 samples for mean

```{r}
reps_20 <- 20

# generates a sampling distribution for the mean of a sample with the specified parameters
sample_dist_mean_20 <- do(reps_20) * mean(rnorm(n = 100, mean = 2, sd = 4))
print(se_20 <- sd(sample_dist_mean_1000$mean))
```

## In-Class Exercise #2

### t-distribution

\<30, "low" degrees of freedom

```{r}
plotDist("t", df = 99, xlab = "x", ylab = "Frequency", col = "#bf5700")
```

### t

```{r}

```

### t

```{r}

```

### t

```{r}

```

### t

```{r}

```

### t

```{r}

```

### t

```{r}

```
