---
title: "2025-02-18"
author: "John Hinkle"
format: html
editor: visual
---

# February 18th, 2025 Notes

## In

```{r}
library(mosaic)
mu <- 10 # "mean" parameter
sigma <- 2 # "standard deviation" parameter
plotDist("norm", mean=mu, sd=sigma, xlab="x", ylab="Frequency")
```

## Draw a random sample of 10 out of the normal distribution

```{r}
s1 <- rnorm (n = 10, mean = 10, sd = 2)
mean(s1) # the mean of the random sample
```

## Draw a random sample of 10 out of the Poisson distribution

```{r}
s2 <- rpois(n = 10, lambda = 10)
mean(s2)
```

## Sampling distributions

```{r}
# number of replicates
reps <- 500

# generates a sampling distribution for the mean of a sample with the specified parameters
samp_dist_mean <- do(reps) * mean(rnorm(n = 10, mean = 10, sd = 2))

# generates a sampling distribution for the median of a sample with the specified parameters
samp_dist_median <-do(reps) * median(rnorm(n = 10, mean = 10, sd = 2))

```

## Plot histograms of sample distributions for stats

Sample size influences error of estimating mean (and median). Larger sample = narrower distribution/less error.

```{r}
# mean
histogram(samp_dist_mean$mean)

# median
histogram(samp_dist_median$median)
```

## Standard deviation and standard estimate based on a sample

```{r}
x <- rnorm(n = 10, mean = 10, sd = 2)
sd <- sd(x)
se <- sd/sqrt(length(x))
print(paste("The standard deviation is", sd))
print(paste("The standard error is", se))
```

## title

```{r}

```

## title

```{r}

```

## title

```{r}

```

## title

```{r}

```

## title

```{r}

```
